Return of the Linguist:\\Toward scalable parallel corpus generation for machine translation

### 2016-06-27 doc/paper.tex
seriously? they EXTENDED the deadline by 2 weeks...

As early as Jelinek's (in)famous quote during the 1980's that ``{\em Every time I fire a linguist, my performance goes up},'' both linguists and linguistics have been increasingly marginalized in natural language processing (NLP). 
More recently, for example, \mynewcite{collobert:2011} mention the possibility ``{\em [ideally]...to learn from letter sequences rather than words},'' illustrating an AI-motivated desire to move away from even the most fundamental of linguistic concepts.
A specific instance of this overall trend is the gradual shift of machine translation (MT) away from classical linguistic rule-based approaches to contemporary machine learning approaches \mycitep{hutchins:2005}, which underlie statistical phrase-based systems like Moses \mycitep{moses} and more recent neural network systems \mycitep{sutskever:2014,bengio:2014}.  
But in the end, even the most cutting-edge machine learning MT system relies crucially on multilingual parallel corpora, typically taken from external sources like multilingual parliamentary proceedings. 
This results in what we perceive to be a disproportionate amount of effort being dedicated to the machine learning component of machine translation, with input corpora being treated almost as an afterthought.\footnote{
    Of course, these parallel corpora represent hundreds of translator-hours of work. 
    However, such translations are optimized for human consumption, not machine learning, with no regard for such niceties as sentence alignment.
    \amtaonly{This is illustrated briefly in Section \ref{subsec:case_study}.}
    }
% TODO: modernization of corpus acquisition / bring machine learning to bear here too

@@

% TODO (AMTA padding?): it's rather like having an athlete with an Olympic-level modern training regimen, when it comes to diet/nutrition, they'll just eat whatever they can find on the streets.
% Long and rich tradition of decades, if not centuries of linguists, "chefs" - want to exploit this somehow
% fueled by data

@@

% although it is ``concrete'', this section will probably be the first to get cut if I run OVER length (which had previously been unimaginable, but is starting to look more and more likely)
% this is some stupid little side note I just noticed a couple weeks ago, but it is expanding to a huge size, because it's like the only concrete ``positive'' result I have...
\amtaonly{
\subsection{Case Study}
\label{subsec:case_study}

% To find an example of suboptimally translated parallel corpora in the literature, one need not look far.
% TODO: summarize this in a footnote for emnlp? is there room?
As an example of suboptimal parallel corpora being used for machine translation, consider the official Chinese to English baseline translation of the {\small \tt tst2010} data set\footnote{https://wit3.fbk.eu/score.php?release=2014-01} from the TED talks corpus, described in greater detail in Section \ref{sec:experiments}.
As a very crude way of assessing translation quality, we used the official evaluation software MultEval \mycitep{multeval} to compute scores for each translated line individually.
Upon manual inspection, the worst scoring individual lines (with TER scores over 150\%) were almost all found to correspond to poor human translations on the Chinese side of the gold corpus.\footnote{
    High TER scores indicated misaligned sentences as well as clerical errors.  In particular, the lecture with {\small \tt talkid} 767 had dozens of erroneous lines, in some of the worst cases having the same Chinese sentence copy/pasted three times on the same line. 
    The baseline Moses system tries valiantly, but it ultimately scores poorly for trying to produce a good machine translation of a poor human translation.
    Alternatively, one can interpret these errors as an additional source of noise in the human encoding of English into Chinese.
}
Such translations might suffice for viewing translated videos monolingually, but they are far from ideal for training a machine translation system.

One might expect such errors to be relatively well-tolerated in large training corpora. 
Nevertheless, this is particularly unsettling because the {\small \tt tst2010} data set has been used as the official development/tuning set for the past several IWSLT evaluation campaigns. 
It is also unclear what effect such noisy test corpora have on MT system evaluation and comparison.

In any case, the fact that these errors have persisted this long ({\small \tt tst2010} has been distributed with only minor changes for every IWSLT Chinese-English evaluation campaign since 2012) is a testament to how insidious these errors can be, even for a leading international conference. 
At the very least, this suggests a need for more careful post-editing of bitexts, particularly for development and test corpora.
More ideal, though, would be the creation of parallel corpora for the express purpose of training, tuning, and evaluating data-driven MT systems.

% I guess don't be concrete - don't say it... because then, you have to be more concrete about it...
	% I can elaborate if reviewers ask... but for now, let's just be concise...

% caption should mention that the difference between 
    % ALTHOUGH you would expect that it would improve all models, it's not clear whether...err? hard to be precise here.
%Removing TED talk number 767 (over 200 lines), as well as 15 hand-picked lines with bad TER scores, 
%First, note that the scores improve, which is consistent with the observation that 
% something to keep in mind in case reviewers ask
%This results in a significant TER score change that is almost as large as the score difference between the highest and lowest ranking system from the evaluation campaign.  
%BLEU scores \mycitep{bleu}, on the other hand, did not change much.
% no, omit this, because DUH, if you change the test set, the scores will change. (it's like changing your ruler.)
% table and reference
%\begin{table}[]
%\centering
%\label{table:tst2010}
%\begin{tabular}{|l|l|l|}
%\hline
% & BLEU & TER  \\ \hline
%Full {\small \tt tst2010} & 11.2 & 77.0  \\ \hline
%Purged {\small \tt tst2010} & 11.8 & 71.3  \\ \hline
%%\hline
%%{\small \tt tst2014} &  &   \\ \hline
%% &  &   \\ \hline
%\end{tabular}
%\caption{By comparison, the difference between the baseline TER score and (not shown) } 
%\end{table}
% TODO: table of scores after purging. This is pretty crucial? why?
	% i think i THOUGHT this was crucial because i had to back up my claims concretely...
	% but the claim from the data is tenuous at best - of course the scores change if the test set changes! so WHAT?
	% BESIDES, I tried training and tuning with purged corpora, and the difference was minimal. it's quite possible that people just don't CARE
} % \amtaonly

\amtaonly{

\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{2}{*}{BLEU $\uparrow$}
& baseline & 11.5 & 0.3 & - & - \\
& system 1 & 10.9 & 0.3 & - & 0.00 \\
\hline
\multirow{2}{*}{TER $\downarrow$}
& baseline & 76.0 & 0.8 & - & - \\
& system 1 & 82.8 & 1.0 & - & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}
\caption{\label{tab:scores} Metric scores for all systems generated using MultEval 0.5.1 \mycitep{multeval}: jBLEU V0.1.1 (an exact reimplementation of NIST's mteval-v13.pl without tokenization); Translation Error Rate (TER) V0.8.0. p-values are relative to baseline and indicate whether a difference of this magnitude (between the baseline and the system on that line) is likely to be generated again by some random process (a randomized optimizer). Metric scores are averages over multiple runs. $s_{sel}$ indicates the variance due to test set selection and has nothing to do with optimizer instability.}
\end{table}

\amtaonly{\subsection{Potential Benefits}}
\label{subsec:benefits}

@@

This paper is organized as follows.
Section \ref{sec:related} discusses previous related work,
Section \ref{sec:generator} describes our rudimentary parallel corpus generator,
Section \ref{sec:experiments} gives preliminary results, 
and Section \ref{sec:future} proposes future work.

@@

% these links are too long for EMNLP. TODO: add them as footnotes for AMTA?
% http://www.fb10.uni-bremen.de/anglistik/langpro/kpml/genbank/generation-bank.html
% http://www.fb10.uni-bremen.de/anglistik/langpro/kpml/ genbank/R3b12-English/Docu/ENGLISH-nigel-exerciseset-mismatches-19981209/EX-SET-1.html
In terms of freely available multilingual natural language generators, the most well-developed one we found was KPML \mycitep{kpml}.
But crafting sentences using KPML is a lengthy process, involving a well-developed linguistic theory to explain the surface forms.
In contrast, our primary goal is to generate large parallel corpora of surface forms quickly. 
% This affords us an amount of flexibility as to the method of generation. % redundant and doesn't really flow
% TODO: for our purposes, the linguistic correctness of a generator (hokey hidden structures) is less important than whether it generates well-translated sentences.

@@

\noindent Our system then expands the subject {\small \tt S} and object {\small \tt O} as noun phrases, adding adjectival and participial modifiers as desired. 
Semantic constraints can be imposed from the verb {\small \tt V} as well as externally.
The generator can then vary the template lexically\footnote{Rewrite probabilities were set by hand; a more principled approach might use, say, a generative PCFG parser.} and syntactically, allowing a large number of sentence pairs to be generated from a single template.
We can also trade quantity for quality by adding more literals to the template, in the spirit of example-based MT.

% looks like this is GOING to run over length. save some if not all of this for AMTA, which is going to run way UNDER length
% TODO: maybe these nonsense sentences shed some light as to what is NOT a sensible, ``natural'' sentence...
%\subsection{Simplistic Linguistics}
We adopt an extremely simplistic view of language as nouns, verbs, and their modifications and elaborations.
\amtaonly{
Inspired by early work on transformations by \mynewcite{chomsky}, we focus on declarative indicative present active sentences in the hopes that they can be transformed into other forms in the long run. 
Similarly, although we enforce some semantic constraints, our system generally produces nonsensical sentences like Chomsky's celebrated ``{\em Colorless green ideas sleep furiously.}''
}The fact that verb phrases can also serve as nouns (gerundives) and modifiers (participles) appears to be a major source of syntactic complexity, and we made it a priority to implement participial modifiers.
To capture recursive structures like participles, we adopt a rudimentary tree representation that is something intermediate between constituency and dependency trees, with constituent-like modifiers that also maintain dependency-like links to their targets.
We plan on eventually open-sourcing both our generator code and its accompanying data.

@@

\section{Preliminary Experiments}
\label{sec:experiments}

%\subsection{Methods} % no space? just do one paragraph each?
We now consider training set amplification as a first application, using the Chinese to English MT task of IWSLT 2015 \mycitep{iwslt2015}\emnlponly{.}\amtaonly{, mentioned briefly in Section \ref{subsec:case_study}.}
This task uses the WIT$^3$ corpus \mycitep{wit3}, which consists of multilingual subtitles of TED talks covering a wide variety of subjects. 
The freely available MultiUN corpus \mycitep{multiun} from the OPUS project \mycitep{opus:2012} was also used for comparison.

To investigate the relative effect of our synthetic parallel corpora, we chose a simple baseline system and fixed all other variables.
Namely, we used the baseline configuration of Moses \mycitep{moses} as described in \mycitep{iwslt2015}, with the exception of changing the target language model to KenLM \mycitep{kenlm}, which we found to be faster and stabler at decoding time than IRSTLM \mycitep{irstlm}.
For the remaining unspecified model settings, we used the {\small \tt grow-diag} alignment heuristic recommended by \mynewcite{segmenter:2008} and the {\small \tt mslr-fe} configuration for lexicalized reordering. 
Chinese text was preprocessed using the latest version of the Stanford Segmenter \mycitep{segmenter:2005,segmenter:2008}.
Phrase and lexicalized reordering tables were interpolated using the {\small \tt tmcombine} script included with Moses \mycitep{tmcombine}, with the interpolation tuned on the {\small \tt dev2010} data set.
BLEU scores were computed as described by \mynewcite{iwslt2015} using the IWSLT 2015 progress data set ({\small \tt tst2014}).\footnote{We chose the {\small \tt tst2014} test set to facilitate comparison with published results from both IWSLT 2014 and 2015 in future work.}

% TODO: mention that LM was held constant - since monolingual (even in-domain?) corpora are typically available at large scale
%\subsection{Task}

% TODO: filler for AMTA? used for corpus analysis stanford POS tagger (incomplete bibtex entry?) \mycitep{postagger:2003}

@@

%\subsection{Results}

% yeah sure, let's add Bing/Google results just for kicks, then take them out later

% definitely want 2 tables?
    % one for learning curves, to show that iwslt > zh_zh > multiun - domain overlap is greater

    % one for 100%, to show that the out of domain corpora aren't helping that much. need moar in-domain data (probably)
    % well, maybe i'll do away with this one

    % I guess don't bother showing single-corpus results for zh_zh and multiun, because then I'd have to show MY single-corpus results, which are even more embarrassing than the horribleness I've written up here

% when i actually go and READ the table, it's clear that I don't even want to LOOK at more than one metric. it's information overload.
%\begin{table}
%\centering
%\label{table:tst2010}
%\begin{tabular}{|l|r|r|r|}
%\hline
%                    & BLEU  & NIST & TER    \\ \hline
%IWSLT15 official    & 11.43 & 4.67 & 72.65  \\ \hline
%Our baseline        & 11.54 & 4.43 & 72.43  \\ \hline
%  + OpenSubtitles   & 11.54 & 4.43 & 72.43  \\ \hline
%  + MultiUN         & 11.67 & 4.48 & 72.60  \\ \hline
%  + generated       & 11.46 & 4.39 & 72.51  \\ \hline
%% &  &   \\ \hline
%\end{tabular}
%\caption{}
% 
%\end{table}

@@

\begin{tabular}{|l|r|}
\hline
                    & BLEU   \\ \hline
25\% corpus         &  9.95  \\ \hline
  + 75\%            & \textbf{11.47}  \\ \hline
%  + Subtitles       & 10.57  \\ \hline
  + MultiUN         & 10.76  \\ \hline
  + Generated       &  9.91  \\ \hline
\end{tabular}

\begin{tabular}{|l|r|}
\hline                    & BLEU   \\ \hline
Official            & 11.43  \\ \hline
Our baseline        & 11.54  \\ \hline
%  + Subtitles       & 11.54  \\ \hline
  + MultiUN         & \textbf{11.67}  \\ \hline
  + Generated       & 11.46  \\ \hline
\end{tabular} & % oh this is how you get 2 tables side by side

@@

% TODO: mention that official results are on a slightly different Moses configuration? mehhhhh
\caption{ \label{tab:results} % oh, for reference numbering, label goes INSIDE caption
    (Left) Chinese-to-English BLEU scores for our baseline Moses configuration with phrase and reordering tables trained on a random 25\% subset of the IWSLT15 training corpus and interpolated (+) with tables for the remaining 75\% (\textasciitilde 150K) of the in-domain corpus, the MultiUN corpus (a \textasciitilde 1M line subset), and a synthetic corpus from our generator (\textasciitilde 5M lines).
    (Right) Same as the left, but starting from tables trained on the entire IWSLT15 corpus.
    Official published scores of the IWSLT15 baseline system are also given for comparison.    
    Qualitatively similar trends for NIST and TER scores were also observed (omitted for clarity).
%    The ``baseline'' row gives 
%    MultiUN is actually more data because it has more words per line.
% automatically cleaned version of the en-zh_zh language pair of OpenSubtitles 2016, roughly 1M lines.
% and a similar number of lines from MultiUN, which is actually more words. but it doesn't do as well.
} % caption

@@

Our generated corpora do not yet make a significant impact on the final BLEU score,\footnote{
    The sub-baseline scores shown are for our most recently generated synthetic corpus; scores slightly higher than our baseline have also been obtained on older generated corpora.
    Both of these outcomes seem to be within experimental error bars.
}
indicating that our parallel corpus generator has a long way to go.
Development on our generator has so far focused on ``rule-based'' syntactic diversity and growing a lexical database tailored to the training set. 
Given the resulting scores, a change of direction seems in order; work on harvesting more ``example-based'' templates from the IWSLT15 training corpus is currently in progress.

% TODO: maybe add Bing and Google results, since nobody seems to report these? save this for AMTA? (haha not gonna have room, sucka)

@@

>>>>

As early as Jelinek's (in)famous quote during the 1980's that ``{\em Every time I fire a linguist, my performance goes up},'' both linguists and linguistics have been increasingly marginalized in natural language processing (NLP). 
More recently, for example, \mynewcite{collobert:2011} mention the possibility ``{\em [ideally]...to learn from letter sequences rather than words},'' illustrating an AI-motivated desire to move away from even the most fundamental of linguistic concepts.
A specific instance of this overall trend is the gradual shift of machine translation (MT) away from classical linguistic rule-based approaches to contemporary machine learning approaches \mycitep{hutchins:2005}, which underlie statistical phrase-based systems like Moses \mycitep{moses} and more recent neural network systems \mycitep{sutskever:2014,bengio:2014}.  
But in the end, even the most cutting-edge machine learning MT system relies crucially on multilingual parallel corpora, typically taken from external sources like multilingual parliamentary proceedings. 
This results in what we perceive to be a disproportionate amount of effort being dedicated to the machine learning component of machine translation, with input corpora being treated almost as an afterthought.\footnote{
    Of course, these parallel corpora represent hundreds of translator-hours of work. 
    However, such translations are optimized for human consumption, not machine learning, with no regard for such niceties as sentence alignment.
    \amtaonly{
        This is not unlike an athlete having an Olympic-level training regimen, fueled by food scrounged off the streets.

        An example of suboptimal parallel corpora being used for machine translation is given in Section \ref{subsec:case_study}.
        At the very least, it suggests a need for more careful post-editing of bitexts, particularly for development and test corpora.
        More ideal, though, would be the creation of parallel corpora for the express purpose of training, tuning, and evaluating data-driven MT systems.
    }    
} % footnote
% TODO: modernization of corpus acquisition / bring machine learning to bear here too

@@

@@

%\amtaonly{\subsection{Potential Benefits}}
\label{subsec:benefits} % ha, this works even if it's not a subsection - LaTeX just figures out what sec/subsec it's in

@@

This paper is organized as follows.
Section \ref{sec:related} discusses previous related work,
Section \ref{sec:generator} describes our rudimentary parallel corpus generator,
Section \ref{sec:experiments} gives experimental results, 
and Section \ref{sec:future} proposes future work.

@@

% these links are too long for EMNLP. TODO: add them as footnotes for AMTA?
%

In terms of freely available multilingual natural language generators, the most well-developed one we found was KPML \mycitep{kpml}.
But crafting sentences using KPML is a lengthy process,\amtaonly{\footnote{
    For examples, see http://www.fb10.uni-bremen.de/anglistik/langpro/kpml/genbank/generation-bank.html}} involving a well-developed linguistic theory to explain the surface forms.
In contrast, our primary goal is to generate large parallel corpora of surface forms quickly. 
% This affords us an amount of flexibility as to the method of generation. % redundant and doesn't really flow
% TODO: for our purposes, the linguistic correctness of a generator (hokey hidden structures) is less important than whether it generates well-translated sentences.

@@

\noindent Our system then expands the subject {\small \tt S} and object {\small \tt O} as noun phrases, adding adjectival and participial modifiers as desired. 
Semantic constraints can be imposed from the verb {\small \tt V} as well as externally.
The generator can then vary the template lexically\footnote{
    Rewrite probabilities were set by hand; a more principled approach might use, say, a generative PCFG parser.} and syntactically, allowing a large number of sentence pairs to be generated from a single template.
We can also trade quantity for quality by adding more literals to the template, in the spirit of example-based MT.

% TODO: maybe these nonsense sentences shed some light as to what is NOT a sensible, ``natural'' sentence...
%\subsection{Simplistic Linguistics}
We adopt an extremely simplistic view of language as nouns, verbs, and their modifications and elaborations.
\amtaonly{
Inspired by early work on transformations by \mynewcite{chomsky}, we focus on declarative indicative present active sentences in the hopes that they can be transformed into other forms in the long run. 
Similarly, although we enforce some semantic constraints, our system generally produces nonsensical sentences like Chomsky's celebrated ``{\em Colorless green ideas sleep furiously.}''
}The fact that verb phrases can also serve as nouns (gerundives) and modifiers (participles) appears to be a major source of syntactic complexity, and we made it a priority to implement participial modifiers.
To capture recursive structures like participles, we adopt a rudimentary tree representation that is something intermediate between constituency and dependency trees, with constituent-like modifiers that also maintain dependency-like links to their targets.
We plan on eventually open-sourcing both our generator code and its accompanying data.

@@

\section{Experimental Results}

%\subsection{Methods} % no space? just do one paragraph each?
\amtaonly{\subsection{Training Set Amplification}}
\label{sec:experiments}
We now consider training set amplification as a first application, using the Chinese to English MT task of IWSLT 2015 \mycitep{iwslt2015}\emnlponly{.}\amtaonly{, mentioned briefly in Section \ref{subsec:case_study}.}
This task uses the WIT$^3$ corpus \mycitep{wit3}, which consists of multilingual subtitles of TED talks covering a wide variety of subjects. 
The freely available MultiUN corpus \mycitep{multiun} from the OPUS project \mycitep{opus:2012} was also used for comparison.

To investigate the relative effect of our synthetic parallel corpora, we chose a simple baseline system and fixed all other variables.
Namely, we used the baseline configuration of Moses \mycitep{moses} as described in \mycitep{iwslt2015}, with the exception of changing the target language model to KenLM \mycitep{kenlm}, which we found to be faster and stabler at decoding time than IRSTLM \mycitep{irstlm}.
Since monolingual corpora are typically available at scale, target language models were obtained using the same in-domain monolingual corpus for all runs.
For the remaining unspecified model settings, we used the {\small \tt grow-diag} alignment heuristic recommended by \mynewcite{segmenter:2008} and the {\small \tt mslr-fe} configuration for lexicalized reordering. 
Chinese text was preprocessed using the latest version of the Stanford Segmenter \mycitep{segmenter:2005,segmenter:2008}.
Phrase and lexicalized reordering tables were interpolated using the {\small \tt tmcombine} script included with Moses \mycitep{tmcombine}, with the interpolation optimized on the {\small \tt dev2010} data set.
Following \mynewcite{iwslt2015}, the model was tuned on the {\small \tt tst2010} data set using the MERT procedure included in Moses.
For Table~\ref{tab:results}, BLEU scores were computed as described by \mynewcite{iwslt2015} using the IWSLT 2015 progress data set ({\small \tt tst2014}).\footnote{
    We chose the {\small \tt tst2014} test set to facilitate comparison with published results from both IWSLT 2014 and 2015 in future work.
} % might be nice to throw this sentence into the Table caption, but LATeX chokes on the \footnote{}

@@

@@

\begin{tabular}{|l|r|}
\hline
                    & BLEU   \\ \hline
25\% corpus         &  9.95  \\ \hline
  + 75\%            & \textbf{11.47}  \\ \hline
  + MultiUN         & 10.76  \\ \hline
  + Generated       &  9.91  \\ \hline
\end{tabular}

\begin{tabular}{|l|r|}
\hline                    & BLEU   \\ \hline
Official            & 11.43  \\ \hline
Our baseline        & 11.54  \\ \hline
  + MultiUN         & \textbf{11.67}  \\ \hline
  + Generated       & 11.46  \\ \hline
\end{tabular} & % oh this is how you get 2 tables side by side

@@

% TODO: mention that official results are on a slightly different Moses configuration? mehhhhh
\caption{ \label{tab:results} % oh, for reference numbering, label goes INSIDE caption
    (Left) Chinese-to-English BLEU scores for our baseline Moses configuration with phrase and reordering tables trained on a random 25\% subset of the IWSLT15 training corpus and interpolated (+) with tables for the remaining 75\% (\textasciitilde 150K) of the in-domain corpus, the MultiUN corpus (a \textasciitilde 1M line subset), and a synthetic corpus from our generator (\textasciitilde 5M lines).
    (Right) Same as the left, but starting from tables trained on the entire IWSLT15 corpus.
    Official published scores of the IWSLT15 baseline system are also given for comparison.    
    Qualitatively similar trends for NIST and TER scores were also observed (omitted for clarity).
} % caption

@@

Our generated corpora do not yet make a significant impact on the final BLEU score,\footnote{
    The sub-baseline scores shown are for our most recently generated synthetic corpus; scores slightly higher than our baseline have also been obtained on older generated corpora.
    Both of these outcomes seem to be within experimental error bars.
}
indicating that our parallel corpus generator has a long way to go.
Development on our generator has so far focused on ``rule-based'' syntactic diversity and growing a lexical database tailored to the training set. 
Given the resulting scores, a change of direction seems in order; work on harvesting more ``example-based'' templates from the IWSLT15 training corpus is currently in progress.
\amtaonly{As a first step in this direction, we examine the gold corpora qualitatively.}

% TODO: maybe add Bing and Google results, since nobody seems to report these? save this for AMTA? (haha not gonna have room, sucka)
% but should also add IWSLT-best results if you're doing that - and I don't see the point, unless my results were anywhere NEAR them
% nah, if at all, just mention in a table caption briefly somewhere

% new results for AMTA, and adding the old ``case study''
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\amtaonly{
\subsection{Qualitative Analysis of Corpora}
\label{subsec:case_study}

Consider the official Chinese to English baseline translation of the {\small \tt tst2010} data set\footnote{
    \label{foot:tst2010}https://wit3.fbk.eu/score.php?release=2014-01
}.
As a crude way of assessing translation quality, we used the official evaluation software MultEval \mycitep{multeval} to compute scores for each translated line individually.
Upon manual inspection, the worst scoring individual lines (especially above 150\%) were almost all found to correspond to poor human translations on the Chinese side of the gold corpus.
This is particularly unsettling because the {\small \tt tst2010} data set has been used as the official development/tuning set for the past several IWSLT evaluation campaigns. 
The fact that these errors have persisted this long ({\small \tt tst2010} has been distributed with only minor changes for every IWSLT Chinese-English evaluation campaign since 2012) is a testament to how insidious these errors can be, even for a prominent international workshop.

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|}
\hline
Gold zh & \zh{安德森：是六万美元。} \\ \hline
Gold en & 60,000. \\ \hline
Moses output & CA : That is 60,000 dollars .  \\ \hline
\end{tabular}
\caption{ \label{tab:bad_pair}
   A ``poorly translated'' sentence pair from {\small \tt tst2010}, with a TER score of 250\%.    
}
\end{table}

An example is given in Table~\ref{tab:bad_pair}.
The baseline Moses system tries valiantly, but it ultimately scores poorly for producing a good machine translation of a liberal human translation.
Alternatively, one can interpret these errors as an additional source of noise in the human encoding of English into Chinese.
It is not entirely clear how the MT process is affected by this kind of noise.

The most effective automated ways we found to identify lines in dire need of post-editing were:
\begin{itemize}
\item 
Duplicated Chinese segments on the same line. 
This was presumably caused by having the same sentence displayed at multiple time points in the video subtitles. 
Often, would also indicate passages that were poorly aligned at the sentence level.
Such translations might suffice for viewing translated videos monolingually, but they are far from ideal for training a machine translation system.

\item 
Missing segments (usually English) when compared with the original lecture transcripts online.\footnote{http://www.ted.com/} 
This issue seems to have been introduced in the IWSLT15 Chinese-English corpus. 
When applied to the IWSLT14 corpus, most of these would be ``false positives'' indicating post-editing of musical symbols and other artifacts.
True positives were often indicative of misaligned sentences.
\end{itemize}

\subsection{Experiments on Post-Edited Corpora}
\label{subsec:post_edited}

% SLIGHTLY inconsistent formatting, since now I have discussion ABOVE the table instead of below...
% but this creates a natural break for the discussion 
Table~\ref{tab:tst2010} shows the results of ``lightly'' post-editing {\small \tt tst2010}. 
On the Chinese side, duplicated segments, applause lines, and translator notes were removed. 
Speaker annotations were normalized on both sides, as well as sentence alignments wherever possible.
Small but noticeable differences in scores are observed. 
(By comparison, the difference between the best and worst scoring Chinese-to-English systems in IWSLT14 \mycitep{iwslt2014} was 6 BLEU points and 7 TER points.)
In this case, the post-edited tuning set seems to guide the MERT optimization procedure of Moses to a slightly different local optimum.

% my baseline - 2016-05-15-213619
% tst2010 fixed lite - 2016-06-17-131927
\begin{table}[ht]
\centering
\begin{tabular}{|l|r|r|r|}
\hline
                    & BLEU  & NIST & TER    \\ \hline
(a) Official IWSLT15    & 11.43 & \textbf{4.67} & 72.65  \\ \hline
(b) Our baseline        & 11.54 & 4.43 & \textbf{72.43} \\ \hline
(c) Post-edited {\small \tt tst2010} & \textbf{11.91} & 4.33 & 75.34 \\ \hline
% &  &   \\ \hline
\end{tabular}
    % TODO: fairly labor intensive, not THAT much payoff? but there is definitely a payoff, and if you could crowd-lever it...

\caption{ \label{tab:tst2010}
    Chinese-to-English translation scores evaluated on the {\small \tt tst2014} data set, with experimental parameters as described in Section~\ref{sec:experiments}. 
    (a) Official published IWSLT15 baseline scores \mycitep{iwslt2015}, for comparison.
    (b) Our baseline Moses configuration, which uses KenLM instead of IRSTLM, as described previously.
    (c) Same as (b), but with a post-edited tuning set {\small \tt tst2010}. 
} % caption
\end{table}

For the rest of this section, we show the results of applying the same post-editing procedure to the test and training sets as well, with the additional step of restoring missing segments for both languages. 
To preserve the integrity of {\small \tt tst2014}, evaluation is now performed using MultEval \mycitep{multeval} on the {\small \tt tst2010} data set itself, with the MERT procedure tuned on the {\small \tt dev2010} data set instead.
These are the data sets and evaluation software used by the official benchmark cited in footnote \ref{foot:tst2010}.
MultEval has the added benefit of providing bootstrapped error bar estimates.

% TODO TODO TODO: rerun these jobs with GIZA++ instead of mgiza! TINY difference in error bars, but should try to be as careful as possible
    % I suppose I MIGHT consider this if the paper is ACCEPTED, haha
\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{2}{*}{BLEU $\uparrow$}
& baseline & 11.5 & 0.3 & - & - \\
& system 1 & 10.9 & 0.3 & - & 0.00 \\
\hline
\multirow{2}{*}{TER $\downarrow$}
& baseline & 76.0 & 0.8 & - & - \\
& system 1 & 82.8 & 1.0 & - & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}
\caption{\label{tab:scores} Metric scores for all systems generated using MultEval 0.5.1 \mycitep{multeval}: jBLEU V0.1.1 (an exact reimplementation of NIST's mteval-v13.pl without tokenization); Translation Error Rate (TER) V0.8.0. p-values are relative to baseline and indicate whether a difference of this magnitude (between the baseline and the system on that line) is likely to be generated again by some random process (a randomized optimizer). Metric scores are averages over multiple runs. $s_{sel}$ indicates the variance due to test set selection and has nothing to do with optimizer instability.}
\end{table}

Input-domain noise can play a role similar to regularization in machine learning - get a reference from denoising autoencoders?
We do indeed find that making the tuning set translations more literal also tends to decrease performance, but this could be because of premature stopping.
Also, the amount of noise added is generally some small amount of Gaussian noise, and it is unclear

For tst2014, revising the DEV set tst2010 instead leads to different local minima instead. 
A better explanation is that the effect of this amount and kind of noise is ill-defined.

% Data Snooping - dedicate this to its own section, to make clear that these are not ``REAL'' results
% we perform snooping on a dedicated snooping set (as if that makes it right...)

@@

% TODO: SMT as dynamic-length or variable-length EBMT. just a qualitative observation of mine...but I suppoose, thinking about SMT mechanistically, that's what it is, really
